Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-02-03 paper.tex
Item 23: Reworded the caption of Figure 4 to more accuratly describe the situation

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement_impedanceVsFrequency_magnitude}
    \end{center}
    \caption{Magnitude of CPE impedance versus frequency of a sine wave stimulus for six concentrations of PBS. Traces represent simulated data while markers represent measured values.}
    \label{fig:CPE_Magnitude}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement_impedanceVsFrequency_phase}
    \end{center}
    \caption{Phase shift across the CPE versus frequency of a sine wave stimulus for six concentrations of PBS. Traces represent simulated data while markers represent measured values.}
    \label{fig:CPE_Phase}
\end{figure}

@@

4. In the legend of Fig 4 and in paragraph below, you say this is magnitude of the CPE. But surely it is not since the sloping lines become horizontal. It is the CPE in series with something. But what is this something? Is it the total series resistance or have you already subtracted the volume resistance (found in section II)?\\
{\color{OliveGreen}
    Item 23\\
    {\color{Red} Reword the caption of Fig. 4 to include the series resistance.}
    No response yet.
}\\

>>>>

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement_impedanceVsFrequency_magnitude}
    \end{center}
    \caption{Magnitude of interfacial impedance between electrodes 2 and 7 against the frequency of a sine wave stimulus for six concentrations of PBS. The slope of the CPE is visible the left, whereas the resistance due to the solution bulk appears on the right. Traces represent simulated data while markers represent measured values.}
    \label{fig:CPE_Magnitude}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement_impedanceVsFrequency_phase}
    \end{center}
    \caption{Phase data of interfacial impedance across electrodes 2 and 7 against frequency of a sine wave stimulus. Traces represent simulated data while markers represent measured values.}
    \label{fig:CPE_Phase}
\end{figure}

@@

4. In the legend of Fig 4 and in paragraph below, you say this is magnitude of the CPE. But surely it is not since the sloping lines become horizontal. It is the CPE in series with something. But what is this something? Is it the total series resistance or have you already subtracted the volume resistance (found in section II)?\\
{\color{OliveGreen}
    Item 23\\
    {\color{Red} Reword the caption of Fig. 4 to include the series resistance.}
    Thank you, have reworded the caption in Figure 4 to more accuratly describe the situation.
}\\
